Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-13 paper/ijcai/paper.tex
another comment, intro

Model-based software diagnosis (MBSD) and Spectrum-Based Fault Localization
(\sfl{}) are two very popular techniques that leverage different principles
to automate fault isolation. An example of a MBSD is Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576}
as wel as some work  \Rui{Cite Wolgang Mayer, ASE2008, IJCAI, DX, ... as well as
some works of Wotawa}, a technique that traces back statements
in the code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
does not analyze code. Instead, it is a black-box, statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., methods) based on coverage information gathered
during the execution of test cases as well as the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements and produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques \Rui{my SAC 2008, DX}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
ranks the relevant parts of the code.

>>>>

Model-based software diagnosis (MBSD) \Rui{cite de kleer, reiter} and Spectrum-Based Fault Localization
(\sfl{}) are two very popular techniques that leverage different principles
to automate fault isolation. An example of a MBSD is Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576}
as wel as some work  \Rui{Cite Wolgang Mayer, ASE2008, IJCAI, DX, ... as well as
some works of Wotawa}, a technique that traces back statements
in the code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
does not analyze code. Instead, it is a black-box, statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., methods) based on coverage information gathered
during the execution of test cases as well as the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements and produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques \Rui{my SAC 2008, DX}.
Intuitively, \ds{} identifies irrelevant parts of the code whereas \sfl{}
ranks the relevant parts of the code.
